Population Differentiation Analysis

### 2017-06-30 doc/RMD/mlg-mcg.Rmd
update documents to shush

```{r load_packages}
library('igraph')
library('ggraph')
library('tidyverse')
library('poppr')
library('viridis')
library('visNetwork')
```

@@

```{r barplots, fig.width = 5, fig.height = 10}
mcg_graph <- mcgs %>% 
  filter(MLGs > 1) %>%
  gather(type, count, MLGs, Samples, -Evenness) %>%
  arrange(desc(type), count) %>%
  rename(Type = type) %>%
  mutate(MCG = forcats::fct_inorder(MCG, ordered = TRUE)) %>%
  ggplot(aes(x = MCG, y = count, group = Type, fill = Type, alpha = Evenness)) +
  geom_col(aes(width = ifelse(Type == "MLGs", 0.5, 0.85)), color = "black", position = "identity") +
  # annotate(geom = "text", x = 18, y =35, 
  #          label = sprintf("Mean Evenness: %.3f", mean(mcgs$Evenness, na.rm = TRUE))) +
  scale_fill_manual(values = c("black", "white")) +
  scale_y_continuous(expand = c(0, 2)) +
  theme_minimal(base_size = 16, base_family = "Helvetica") +
  coord_flip() +
  theme(panel.grid.major.y = element_blank()) +
  theme(legend.box.just = "left") +
  theme(legend.box.margin = unit(c(0, 0.55, 11, 0), "lines")) +
  theme(legend.box.background = element_rect(fill = NA, color = "black")) +
  # theme(legend.box = "horizontal") +
  theme(aspect.ratio = 2) +
  labs(list(
    alpha = "MLG\nEvenness"
  ))

>>>>

```{r load_packages, message = FALSE, warning = FALSE}
library('igraph')
library('ggraph')
library('tidyverse')
library('poppr')
library('viridis')
library('visNetwork')
```

@@

```{r barplots, fig.width = 5, fig.height = 10}
mcg_graph <- mcgs %>% 
  filter(Samples > 1) %>%
  gather(type, count, MLGs, Samples, -Evenness) %>%
  arrange(desc(type), count) %>%
  rename(Type = type) %>%
  mutate(MCG = forcats::fct_inorder(MCG, ordered = TRUE)) %>%
  ggplot(aes(x = MCG, y = count, group = Type, fill = Type, alpha = Evenness)) +
  geom_col(aes(width = ifelse(Type == "MLGs", 0.5, 0.85)), color = "black", position = "identity") +
  # annotate(geom = "text", x = 18, y =35, 
  #          label = sprintf("Mean Evenness: %.3f", mean(mcgs$Evenness, na.rm = TRUE))) +
  scale_fill_manual(values = c("black", "white")) +
  scale_y_continuous(expand = c(0, 2)) +
  theme_minimal(base_size = 16, base_family = "Helvetica") +
  coord_flip() +
  theme(panel.grid.major.y = element_blank()) +
  theme(legend.box.just = "left") +
  theme(legend.box.margin = unit(c(0, 0.55, 11, 0), "lines")) +
  theme(legend.box.background = element_rect(fill = NA, color = "black")) +
  # theme(legend.box = "horizontal") +
  theme(aspect.ratio = 2) +
  labs(list(
    alpha = "MLG\nEvenness"
  ))

### 2017-06-30 doc/RMD/pop-diff.Rmd
update documents to shush

---
title: "Population Differentiation Analysis"
output: 
  html_notebook:
    toc: true
---

@@

```{r load_packages}
library('tidyverse')
library('poppr')
library('ggcompoplot')
```

>>>>

---
title: "Population Differentiation Analysis"
output: 
  html_notebook:
    toc: true
editor_options: 
  chunk_output_type: inline
---

@@

```{r load_packages, warning = FALSE, message = FALSE}
library('tidyverse')
library('poppr')
library('ggcompoplot')
```
